Vragenlijst thesis evaluatie

### 2015-04-03 Thesisfollowup/ThesisFollowUpSophieMarien.tex

\section{Vergelijk wat je gedaan hebt met het opgestelde werkplan. Hoever sta je? Moet het werkplan aangepast worden?}
\section{Schrijf een eerste versie van een hoofstuk over een afgewerkte bijdrage van je masterproef.}
Dit is meegegeven in bijlage
\section{Geef een korte inhoud van het tweede artikel dat je gaat schrijven. (Dit is niet van toepassing voor de studenten van de Master Toegepaste Informatica)}
Het tweede artikel gaat gaan over mijn implementatie van FlipIt op een bedrijfsnetwerk. Eerst bespreek ik hoe ik FlipIt aanpas. Daarna stel ik een methode voor via matrices om de propagatie van een virus te beschrijven. De methode die gebruikt wordt is gelijkaardig aan die van Google Page Ranking. Via deze functie kan ik de totale controle berekenen van een speler over een spel. In het artikel leg ik de methode uit aan de hand van een default spel.
\section{Beschrijf in 10 lijnen de demo die je bij je verdediging zult geven.}
Ik heb een theoretische thesis dus kan ik moeilijk een demo geven. Ik zal enkele voorbeelden uitwerken om mijn werkingsmethode uit te leggen.
\section{Wat is er afgesproken met je begeleider en/of promotor om op te leveren als major milestone die het praktische werk van je thesis afsluit?}

\section{Evalueer de tijd die je in je thesis gestoken hebt in de voorbije 4 weken: veel te weinig / te weinig / voldoende / ruim voldoende / meer dan verwacht.}
Ik heb voldoende tijd in mijn thesis gestoken. 
\section{Evalueer de vorderingen van je thesis t.o.v. het bereiken van de vooropgestelde doelstelling: ver achter op het schema / achter op het schema / goed op schema / vooruit op het schema / ver vooruit op het schema.}
\section{Stuur de ingevulde timesheet mee als bijlage.}

>>>>

\section{Vergelijk wat je gedaan hebt met het opgestelde werkplan. Hoever sta je? Moet het werkplan aangepast worden?}
Ik moet een tandje bijsteken en al verder beginnen schrijven. Ik was vergeten in mijn werkplan bij te steken dat ik een week op Athens ging gaan. 
\section{Schrijf een eerste versie van een hoofstuk over een afgewerkte bijdrage van je masterproef.}
Dit is meegegeven in bijlage. Ik heb ineens heel mijn voorlopige thesistekst in bijlage gestoken. 
\section{Geef een korte inhoud van het tweede artikel dat je gaat schrijven. (Dit is niet van toepassing voor de studenten van de Master Toegepaste Informatica)}
Het tweede artikel gaat gaan over mijn implementatie van FlipIt op een bedrijfsnetwerk. Eerst bespreek ik hoe ik FlipIt aanpas. Daarna stel ik een methode voor via matrices om de propagatie van een virus te beschrijven. De methode die gebruikt wordt is gelijkaardig aan die van Google Page Ranking. Via deze functie kan ik de totale controle berekenen van een speler over een spel. In het artikel leg ik de methode uit aan de hand van een default spel. 
Ook geef ik een eerste setting van een spel en de bijhorende benefit formules waaruit ik al dan niet een equilibrium kan bepalen.
\section{Beschrijf in 10 lijnen de demo die je bij je verdediging zult geven.}
Ik heb een theoretische thesis dus kan ik moeilijk een demo geven. Ik zal enkele voorbeelden uitwerken om mijn werkingsmethode uit te leggen.
\section{Wat is er afgesproken met je begeleider en/of promotor om op te leveren als major milestone die het praktische werk van je thesis afsluit?}
Dit is nog niet afgesproken.
\section{Evalueer de tijd die je in je thesis gestoken hebt in de voorbije 4 weken: veel te weinig / te weinig / voldoende / ruim voldoende / meer dan verwacht.}
De voorbije weken heb ik minder dan voldoende aan mijn thesis gewerkt. Ik liep vast op een aantal zaken en ik ben een week op Athens cursus geweest. 
\section{Evalueer de vorderingen van je thesis t.o.v. het bereiken van de vooropgestelde doelstelling: ver achter op het schema / achter op het schema / goed op schema / vooruit op het schema / ver vooruit op het schema.}
Ik loop een beetje achter op schema want ik had toch graag nu al een aantal formuleringen bepaald en een model uitgewerkt.
\section{Stuur de ingevulde timesheet mee als bijlage.}

### 2015-04-03 Thesisfollowup/thesisfollowup.tex

\begin{titlepage}
\title{Thesis Follow Up}
\author{Sophie Marien}
\date{} 
\end{titlepage}

@@

\section{Vergelijk wat je gedaan hebt met het opgestelde werkplan. Hoever sta je? Moet het werkplan aangepast worden?}
Ik moet een tandje bijsteken en al verder beginnen schrijven. Ik was vergeten in mijn werkplan bij te steken dat ik een week op Athens ging gaan. 
\section{Schrijf een eerste versie van een hoofstuk over een afgewerkte bijdrage van je masterproef.}
Dit is meegegeven in bijlage. Ik heb ineens heel mijn voorlopige thesistekst in bijlage gestoken. 
\section{Geef een korte inhoud van het tweede artikel dat je gaat schrijven. (Dit is niet van toepassing voor de studenten van de Master Toegepaste Informatica)}
Het tweede artikel gaat gaan over mijn implementatie van FlipIt op een bedrijfsnetwerk. Eerst bespreek ik hoe ik FlipIt aanpas. Daarna stel ik een methode voor via matrices om de propagatie van een virus te beschrijven. De methode die gebruikt wordt is gelijkaardig aan die van Google Page Ranking. Via deze functie kan ik de totale controle berekenen van een speler over een spel. In het artikel leg ik de methode uit aan de hand van een default spel. 
Ook geef ik een eerste setting van een spel en de bijhorende benefit formules waaruit ik al dan niet een equilibrium kan bepalen.
\section{Beschrijf in 10 lijnen de demo die je bij je verdediging zult geven.}
Ik heb een theoretische thesis dus kan ik moeilijk een demo geven. Ik zal enkele voorbeelden uitwerken om mijn werkingsmethode uit te leggen.
\section{Wat is er afgesproken met je begeleider en/of promotor om op te leveren als major milestone die het praktische werk van je thesis afsluit?}
Dit is nog niet afgesproken.
\section{Evalueer de tijd die je in je thesis gestoken hebt in de voorbije 4 weken: veel te weinig / te weinig / voldoende / ruim voldoende / meer dan verwacht.}
De voorbije weken heb ik minder dan voldoende aan mijn thesis gewerkt. Ik liep vast op een aantal zaken en ik ben een week op Athens cursus geweest. 
\section{Evalueer de vorderingen van je thesis t.o.v. het bereiken van de vooropgestelde doelstelling: ver achter op het schema / achter op het schema / goed op schema / vooruit op het schema / ver vooruit op het schema.}
Ik loop een beetje achter op schema want ik had toch graag nu al een aantal formuleringen bepaald en een model uitgewerkt.
\section{Stuur de ingevulde timesheet mee als bijlage.}

>>>>

\begin{titlepage}
\title{Thesis followup}
\author{Sophie Marien}
\end{titlepage}

@@

\section{Vergelijk wat je gedaan hebt met het opgestelde werkplan. Hoever sta je? Moet het werkplan aangepast worden?}
\section{Schrijf een eerste versie van een hoofstuk over een afgewerkte bijdrage van je masterproef.}
\section{Geef een korte inhoud van het tweede artikel dat je gaat schrijven. (Dit is niet van toepassing voor de studenten van de Master Toegepaste Informatica)}
\section{Beschrijf in 10 lijnen de demo die je bij je verdediging zult geven.}
\section{Wat is er afgesproken met je begeleider en/of promotor om op te leveren als major milestone die het praktische werk van je thesis afsluit?}
\section{Evalueer de tijd die je in je thesis gestoken hebt in de voorbije 4 weken: veel te weinig / te weinig / voldoende / ruim voldoende / meer dan verwacht.}
\section{Evalueer de vorderingen van je thesis t.o.v. het bereiken van de vooropgestelde doelstelling: ver achter op het schema / achter op het schema / goed op schema / vooruit op het schema / ver vooruit op het schema.}
\section{Stuur de ingevulde timesheet mee als bijlage.}

### 2015-04-03 doc/template/chap-3.tex

\section{Literatuurstudie}
\begin{description}
\item Distributed Worm Simulation with a REalistic Internet 2005  \\
Modeling of congestions of network through worm propagation. Mathematical model focussing on the underlying network infrastructure.(diff no game theory) 
\item Of threats and Costs: A Game-theoretic approach to security risk managment 2013\\
Model network security of networks with a non-cooperative node through game theory. Attacker knows the defense strategies and the defender has knowledge of the possible attacks. Each actor considers the actions of the other before deciding to strive to optimize their own utility. (diff not stealthy)
\item Game theory meet network security and privacy (2013) \\
Chapter 3 addresses several games in game theory for modeling network security.
\item Game theoretic approach for cost-benefit analysis of malware proliferation prevention (..)
Introduces SIS and SIR together with 'patch', 'removal' and 'patch and removal'.
\end{description}

@@

\section{Why Game Theory to model security problem}
Actors in a security protocol must follow the systems and some arbitrarily actors that are malisious and do not follow the protocol. [Bridging GameTheory and Cryptography]. Gametheoretic approach proposes a model where all the actors act with self-interest.

@@

Company networks are targeted. It costs a lot. They want to defend their company networks. No loss of data, integrity and confidentiality.  Many ways to attack a company. Virusses, trojans, worms, DOS, .. Hard to protect against every attacker.

>>>>

\section{Gametheory}

Game theory is the study between self interested agents and the actions they perform. self interested agents means not that they want to harm each other or that they only care about themselves. Agent has a description of the world he likes. A utility function is a mapping of the world that the agent likes to real numbers.

\section{Literatuurstudie}

Difference with FlipThem: sub part of nodes for control and strategy difference: dependant of grade of the nodes, instead of just periodic.
- Literatuurstudie
- Flipit
- Game Motivation
- Formal definition

\begin{description}
\item Distributed Worm Simulation with a Realistic Internet 2005  \\
Modelling of congestions of network through worm propagation. Mathematical model focussing on the underlying network infrastructure.(diff no game theory) 
\item Of threats and Costs: A Game-theoretic approach to security risk management 2013\\
Model network security of networks with a non-cooperative node through game theory. Attacker knows the defence strategies and the defender has knowledge of the possible attacks. Each actor considers the actions of the other before deciding to strive to optimize their own utility. (diff not stealthy)
\item Game theory meet network security and privacy (2013) \\
Chapter 3 addresses several games in game theory for modelling network security.
\item Game theoretic approach for cost-benefit analysis of malware proliferation prevention (..)
Introduces SIS and SIR together with 'patch', 'removal' and 'patch and removal'.
\end{description}

@@

\section{Why Game Theory to model security problem}
Actors in a security protocol must follow the systems and some arbitrarily actors that are malicious and do not follow the protocol. [Bridging Game Theory and Cryptography]. Game theoretic approach proposes a model where all the actors act with self-interest.

@@

Company networks are targeted. It costs a lot. They want to defend their company networks. No loss of data, integrity and confidentiality.  Many ways to attack a company. Viruses, Trojans, worms, DOS, .. Hard to protect against every attacker.

### 2015-04-03 doc/template/intro.tex

Security is an important asset in the computer science. Technology is growing fast and so are the malicious people. Defending a network of a company is not very easy. It makes use of firewalls, routers, IDS systems, virus scans, and so on. Protecting a company network is difficult job. They are often the victim of targetted attacks. In a security report of 2014, \todo{verwijzing naar report}, state that 80\% of the companies are the vitims of targeted attacks. 
Many corporate networks have to continuously defend themselves against outside invaders such as viruses and worms. The network administrator will try to keep the network to malware-free as possible. If still there is an intruder managed to penetrate the network then the network manager this intruder trying to get out as quickly as possible. This is not always easy. Especially when the intruders secretly sneak and then spread rapidly.
In this paper we will work further on the work made by Marten van Dijk, Ari Juels, Alina Oprea and Ronals L. Rivest \todo{verwijzing naar FlipIT} who wrote a report on the Game FlipIt. FlipIt is a the game of '' Stealthy Takeovers''. It models a game by means of two players, the attacker and the defender. Both can gain control over a single shared resource by flipping it. The most important property of the game is that the flipping happens stealthy. This means that the players have no clue about when the other player moves. The goal of the game is to maximise the time the player controls the resource minus the average cost of the flipping.

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:

>>>>

Security is an important asset in Computer Science. Defending a network of a company is not an easy job. To prevent intruders it can make use of firewalls, routers, IDS systems, virus scans, and other defence mechanisms. Unfortunately technology is growing fast and attacks are getting more sophisticated and the causes of these attacks can be very different. \todo{iets tussen nog} Companies are often the victim of targeted attacks. In a security report of 2014, \todo{verwijzing naar report}, states that 80\% of the companies are the victims of targeted attacks. Many companies don't see themselves as a target, but sometimes they might be collateral, the target on the way to the real target. This means that everybody can be a target. 
Corporate networks should continuously defend themselves against outside invaders such as viruses and worms. By doing so the network administrator can keep the network as malware-free as possible. If there is  an intruder managed to penetrate the network then the network manager this intruder trying to get out as quickly as possible. This is not always easy. Especially when the intruders secretly sneak and then spread rapidly.
In this paper we will work further on the work made by Marten van Dijk, Ari Juels, Alina Oprea and Ronals L. Rivest \todo{verwijzing naar FlipIT} who wrote a report on the Game FlipIt. FlipIt is a the game of '' Stealthy Takeovers''. It models a game by means of two players, the attacker and the defender. Both can gain control over a single shared resource by flipping it. The most important property of the game is that the flipping happens stealthy. This means that the players have no clue about when the other player moves. The goal of the game is to maximise the time the player controls the resource minus the average cost of the flipping.

@@

\section{introduction number 2}

(We live in an era) In this era where digitalization becomes prominent in every aspect of our lives, where technology is growing fast and where business are always under attack, security becomes an issue of increasing complexity. Since 2009, the number of reported security attacks has increased 66\%, year over year. \todo{security report van pwc}. These numbers only represent the attacks that are detected. In 2014 117,339 attacks where coming in daily. Many of those attacks have a different cause. Some of them can be benign, others can be harmful. Many companies are unaware of all the attacks. Some of them think that they are not a target, but they might be a target on the way to a real target. Recently there where some high profiled targeted attacks which have been revealed. (Belgacom). 
Targeted attacks are ...
The \textit{Kill Chain} is a concept by Lockheed Martin Corporation, explained in the whitepaper \todo{withepaper toevoegen}. It explains the different phases of a typical attack from the view of an attacker. It also outlines the typical attacker activities on the right. This model is very useful to define the different moments of the life cycle of an attack and when a company should act to defend itself. In this paper we would like to prevent the viruses of spreading into the network system of a company. This means that we have to act in phase Installation, Command and Control and Action on Objectives of the kill chain.

  Security is an important asset in Computer Science. Defending a network of a company is not an easy job. To prevent intruders it can make use of firewalls, routers, IDS systems, virus scans, and other defence mechanisms. Unfortunately technology is growing fast and attacks are getting more sophisticated and the causes of these attacks can be very different. \todo{iets tussen nog} Companies are often the victim of targeted attacks. In a security report of 2014, \todo{verwijzing naar report}, states that 80\% of the companies are the victims of targeted attacks. Many companies don't see themselves as a target, but sometimes they might be collateral, the target on the way to the real target. This means that everybody can be a target. 
Corporate networks should continuously defend themselves against outside invaders and targeted attacks. Researchers have already investigated the situations through the FlipIt game in which a system is continuously compromised by an attacker through targeted attacks. 
FlipIt is a the game of '' Stealthy Takeovers''. It models a game by means of two players, the attacker and the defender. Both can gain control over a single shared resource by flipping it. The most important property of the game is that the flipping happens stealthy. This means that the players have no clue about when the other player moves and has control over the shared resource. The goal of the game is to maximise the time the player controls the resource minus the average cost of the number of flipping.
In this paper we model a company network through multiple shared resources and a flip from the attacker that drops a virus that will spread itself autonomously. We show that ...
%http://www.pwc.com/gx/en/consulting-services/information-security-survey/index.jhtml
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis"
%%% End:
